---
title: "Unit 04-MSDS Doing Data Science"
author: "Eduardo Cantu Medellin"
date: "February 2, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## FiveThirtyEight Data
Navigate on GitHub to https://github.com/rudeboybert/fivethirtyeight and read README.md. Seriously, it will include everything you need. 
	•	Install the fivethirtyeight package.  
	•	In the listing of Data sets in package ‘fivethirtyeight,’ assign the eighteenth data set to an object ‘df.’  
	•	Use a more detailed list of the data sets to write out the URL in a comment to the related news story.  
	•	Using R command(s), give the dimensions and column names of this data frame.  


```{r fiveThirtyEightData}
#Loads the "fivethirtyeight" library
library(fivethirtyeight)

#Lists all the data sets for "fivethirtyeight"
data(package="fivethirtyeight")

#Load the eighteenth data set from the fivethirtyeight : "college_recent_grads"
df <- college_recent_grads

#A more detailed list of the datasets
vignette("fivethirtyeight", package = "fivethirtyeight")

#Dimensions and column names for df
dim(df) # Row Columns 
names(df) # Column Names for the data frame

```



## Data Summary  
  
  •	Write an R command that gives you the column names of the data frame.  Right after that, write one that counts the number of columns but not rows.  Hint: The number should match one of your numbers in Question 1d for dimensions.  
	•	Generate a count of each unique major_category in the data frame.  I recommend using libraries to help.  I have demonstrated one briefly in live-session.  To be clear, this should look like a matrix or data frame containing the major_category and the frequency it occurs in the dataset.  Assign it to major_count.  
	•	To make things easier to read, put par(las=2) before your plot to make the text perpendicular to the axis.  Make a barplot of major_count.  Make sure to label the title with something informative (check the vignette if you need), label the x and y axis, and make it any color other than grey.  Assign the major_category labels to their respective bar.  Flip the barplot horizontally so that bars extend to the right, not upward.  All of these options can be done in a single pass of barplot(). Note: It’s okay if it’s wider than the preview pane.  
	•	Write the fivethirtyeight data to a csv file.  Make sure that it does not have row labels.  
  
```{r DataSummary, echo=TRUE}
#Column Names and Column Count for data frame
names(df)  # Column Na
ncol(df)  # Column Count

# Summary
major_count <- table(df$major_category)

as.data.frame(major_count)

#plot
par(las=2)

barplot(major_count, ylab="Category Count", col = "yellow" , ylim=c(0,35))
title(main="Major Category Distribution", font=12)

#horizontal plot
barplot(major_count, xlab="Category Count", col = "yellow" , xlim=c(0,35), horiz = TRUE, space = 1, width = 2)
title(main="Major Category Distribution", font=12)


```

  


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
